Analysis plan

### 2023-04-19 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Adding variable for teams that don't exist during entire period
Update MSG-P2312-Analysis Plan-1-clusters.rmd
More updates for proportion of observation window

@@

Both data sources will be checked for duplication and deduplicated. The
daily check-in data has no true unique identifier. The roster data is
uniquely identified by `employee_e_mail_address` and `snapshot_date`,
but some entries for `employee_e_mail_address` are null. The roster data
*should not* have any duplications on `employee_e_mail_address` and
`snapshot_date`, but this will be checked. To create a unique identifier
in the daily check-in data, we will following process:

@@

@@

@@

>>>>

This work will address the following research questions: 1. What are the
rates of telework since the federal return-to-office transition? 2. Do
telework behaviors match position category (e.g., onsite, offsite, etc.)
in the roster? 3. At what rates do teams work together onsite vs.
remotely? 4. Do the telework patterns of supervisors match the telework
patterns of supervisees?

@@

Both data sources will be checked for duplication and deduplicated. The
daily check-in data has no true unique identifier. The roster data is
uniquely identified by `employee_e_mail_address` and `snapshot_date`,
but some entries for `employee_e_mail_address` are null. The roster data
*should not* have any duplications on `employee_e_mail_address` and
`snapshot_date`, but this will be checked. To create a unique identifier
in the daily check-in data, we will use the following process:

@@

-   Proportion of observation window the team existed

@@

-   Proportion of observation window the team existed.

@@

    -   Proportion of observation window the team exists
